%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 2: ABSTRACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% INPUTS NEEDED: 
%   - All performance metrics from Results sections
%   - Must match: 97.5%, 83.24%, 76%→92%, 40%→90%
%
% FIGURES: None
% TABLES: None
% DEPENDENCIES: Results sections (metrics must match)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract{The success of precision oncology relies on rapid access to genomic variant interpretation. However, current knowledge bases require specialized resources and bioinformatics expertise, employing heterogeneous schemas and complex query interfaces inaccessible to physicians using natural language. Medical geneticists may spend up to 30 minutes per variant analysis, with studies showing low confidence in genomic interpretation among oncologists. To address these barriers, we developed OncoCITE (Curation \& Integration of Traceable Evidence), an auditable AI pipeline that extracts actionable evidence and molecular profiles from oncology literature to build a CIViC-compatible knowledge base and enables natural-language queries. We implemented OncoCITE in three phases. Phase~1 combined the Reason-Action-Conclude-Think (ReACT) paradigm with the DSPy framework and fine-tuned GPT-4.1 on 1,300 human-validated extractions from CIViC, achieving 97.5\% extraction accuracy with full reasoning traces. Phase~2 added a natural-language-to-SQL interface using LoRA-tuned Llama-3 (3B parameters) trained on 21,000 synthetic question--query pairs, achieving 83.24\% execution-correct SQL generation versus 50--55\% for baseline models. Phase~3 incorporated a knowledge-management layer with entity canonicalization and GPT-4.1 multi-step reasoning, increasing end-to-end task success from 76\% to 92\% and synonym/misspelling-heavy query success from 40\% to 90\%. OncoCITE delivers auditable, standards-compatible extraction of molecular oncology evidence and natural-language access, transforming tasks requiring weeks of manual curation into minutes while producing clinician-ready, guideline-aligned outputs.}

\keywords{Precision oncology \and Natural language processing \and Clinical decision support \and Genomic variant interpretation \and Knowledge extraction \and Text-to-SQL \and Automated curation \and AI in healthcare}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT STRUCTURE BREAKDOWN:
%
% SENTENCE 1-2: Problem statement
%   "The success of precision oncology relies on rapid access..."
%   "However, current knowledge bases require specialized resources..."
%
% SENTENCE 3: Clinical impact
%   "Medical geneticists may spend up to 30 minutes per variant..."
%
% SENTENCE 4: Solution introduction
%   "To address these barriers, we developed OncoCITE..."
%
% SENTENCE 5: Implementation overview
%   "We implemented OncoCITE in three phases."
%
% SENTENCE 6: Phase 1 (ReACT extraction)
%   Key metrics: 1,300 extractions, 97.5% accuracy
%
% SENTENCE 7: Phase 2 (NL-to-SQL)
%   Key metrics: 21,000 pairs, 83.24% vs 50-55% baseline
%
% SENTENCE 8: Phase 3 (Knowledge management)
%   Key metrics: 76%→92% overall, 40%→90% synonym queries
%
% SENTENCE 9: Impact statement
%   "OncoCITE delivers auditable, standards-compatible..."
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% METRICS CROSS-REFERENCE CHECKLIST:
%
% □ 1,300 human-validated extractions → Must match Results 2.1, 2.2
% □ 97.5% extraction accuracy → Must match Results 2.2
% □ 21,000 synthetic question-query pairs → Must match Results 2.1, 2.4
% □ 83.24% execution-correct SQL → Must match Results 2.4
% □ 50-55% baseline models → Must match Results 2.4
% □ 76% to 92% task success → Must match Results 2.5
% □ 40% to 90% synonym/misspelling queries → Must match Results 2.5
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
