%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION 10: BACK MATTER
% Acknowledgements, Declarations, Data/Code Availability
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% INPUTS NEEDED: 
%   - Funding information
%   - Author COI statements
%   - Repository URLs
%   - Author contributions
%
% FIGURES: None
% TABLES: None
% DEPENDENCIES: Author list
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\backmatter

%%=============================================================%%
%% SUPPLEMENTARY INFO POINTER
%%=============================================================%%

\bmhead{Supplementary information}

Supplementary information is available for this paper. Supplementary Table~S1 provides additional details on database comparison. Supplementary Table~S2 contains the complete GPRC5D evidence table with all 15 entries. Supplementary Fig.~S3 shows representative examples of terminology canonicalization. Supplementary Methods provides full methodological details including training procedures.

%%=============================================================%%
%% ACKNOWLEDGEMENTS
%%=============================================================%%

\bmhead{Acknowledgements}

S.P. is supported by National Cancer Institute (NCI) R01 CA244899, CA252222 and Tisch Cancer Institute P30 CA196521 grants. The authors thank the CIViC curation team for providing open-access variant annotations that served as training data for this study.

%%=============================================================%%
%% DECLARATIONS
%%=============================================================%%

\section*{Declarations}

%%% FUNDING %%%
\bmhead{Funding}

This work was supported by National Cancer Institute (NCI) grants R01 CA244899 and CA252222 (to S.P.), and Tisch Cancer Institute grant P30 CA196521 (to S.P.). The funders had no role in the design of the study, collection, analysis, and interpretation of data, or in writing the manuscript.

%%% COMPETING INTERESTS %%%
\bmhead{Competing interests}

A.L. reports research support from Celgene/BMS. S.J. is a consultant for Janssen, BMS, Legend Biotech, Regeneron, Caribou, Sanofi, Takeda, and Karyopharm. He is DMC chairman for Genmab and Sanofi. He has membership on an entity's Board of Directors or advisory committees for IMS, ASH, and SOHO. S.P. receives research support from Amgen Inc., Celgene/BMS Corporation, The Multiple Myeloma Research Foundation, GRAIL, and Caribou; he is also on the advisory board for GRAIL and Genentech. M.Q., S.T., and D.S. declare that they have no competing interests.

%%% ETHICS APPROVAL %%%
\bmhead{Ethics approval}

Not applicable. This study involved only publicly available data and computational methods without human participants or animal subjects.

%%% CONSENT %%%
\bmhead{Consent for publication}

Not applicable.

%%% DATA AVAILABILITY %%%
\bmhead{Data availability}

The datasets supporting the results of this article are available in the OncoCITE repository at \url{https://github.com/Ali-Maq/oncodif_public}. The CIViC database used for training is publicly available at \url{https://civicdb.org}. Synthetic training data for the natural language-to-SQL system and comprehensive terminology dictionaries are available in our repository.

%%% CODE AVAILABILITY %%%
\bmhead{Code availability}

OncoCITE source code is available at \url{https://github.com/Ali-Maq/oncodif_public} under MIT License. Requirements: Python 3.9+, DSPy 2.4.0+, PyPDF2, OpenAI API, Fireworks AI API.

%%% AUTHOR CONTRIBUTIONS %%%
\bmhead{Author contributions}

M.Q. and A.L. conceptualized and designed the study. M.Q. implemented the system and performed validation. S.T., S.J., and S.P. provided clinical expertise. A.L. and M.Q. wrote the original draft of the manuscript. All authors reviewed and edited the manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CHECKLIST FOR BACK MATTER:
%
% SUPPLEMENTARY MATERIALS LISTED:
%   □ Table S1 - Database comparison (expanded)
%   □ Table S2 - GPRC5D evidence table (15 entries)
%   □ Figure S3 - Canonicalization examples
%   □ Supplementary Methods
%
% FUNDING GRANTS:
%   □ NCI R01 CA244899 (to S.P.)
%   □ NCI CA252222 (to S.P.)
%   □ Tisch Cancer Institute P30 CA196521 (to S.P.)
%
% COMPETING INTERESTS BY AUTHOR:
%   □ A.L. - Celgene/BMS research support
%   □ S.J. - Multiple consultancies listed
%   □ S.P. - Multiple research support and advisory boards
%   □ M.Q. - No competing interests
%   □ S.T. - No competing interests
%   □ D.S. - No competing interests
%
% REPOSITORY URLS:
%   □ GitHub: https://github.com/Ali-Maq/oncodif_public
%   □ CIViC: https://civicdb.org
%
% SOFTWARE REQUIREMENTS:
%   □ Python 3.9+
%   □ DSPy 2.4.0+
%   □ PyPDF2
%   □ OpenAI API
%   □ Fireworks AI API
%
% AUTHOR CONTRIBUTIONS:
%   □ Conceptualization: M.Q., A.L.
%   □ Implementation: M.Q.
%   □ Validation: M.Q.
%   □ Clinical expertise: S.T., S.J., S.P.
%   □ Writing (original): A.L., M.Q.
%   □ Review/editing: All authors
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
